---
title: "Encode Multistate Outcome"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-amsterdam/libs/css/sidebar.css
    keep_md: yes
    toc: yes
---

This report demonstrates and annotates the computation of the multistate variable used as the outcome in multistate models.

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F}
#Don't combine this call with any other chunk
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/encode-multistate/encode-multistate.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../')
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show',
  message = TRUE,
  comment = NA,
  tidy = FALSE,
  fig.height = 4,
  fig.width = 5.5,
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
messageChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/encode-multistate/encode-multistate.R")
```
<!-- Load 'sourced' R files.  Suppress the output when loading packages. -->
```{r load-packages, echo=echoChunks, message=messageChunks}
```
<!-- Load the sources.  Suppress the output when loading sources. -->
```{r load-sources, echo=echoChunks, message=messageChunks}
```
<!-- Load any Global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echoChunks, results='show', message=messageChunks}
```
<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the code behind file.
```

# (I) Exposition

> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/map/0-ellis-island-map.R`.

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

## (I.A) Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following:

- (1) Reads in raw data file
- (2) Extract, combines, and exports metadata (specifically, variable names and labels, if provided) into `./data/shared/meta/map/names-labels-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta/map/meta-data-map.csv`. They are used by automatic scripts in later manipulation and analysis.  
- (4) Combines unit and meta data into a single DTO to serve as a starting point to all subsequent analyses.   


<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

### Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```

#(II) Development

## Define outcome

The purpose of the transformations annotated in this report is to create a categorical outcome variable that would represent the observed state of the individual at time $t$. Mini-mental state exame (`mmse`) has been chosen to operationalize cognitive impairment. Possible states have been defined as :

* `mmse` $=[27,30]$ --> `state = 1` - no impairment  
* `mmse` $=[23,27)$ --> `state = 2` - mild impairment   
* `mmse` $=[0 :22)$ --> `state = 3` - moderate/severe impairment  
* `state = 4` - dead state  

The covariates of interested include:   

* `age` -  Centered at study specific mean age.   
* `birth cohort` - Birth year (?)  
* `male` -  Males 1, Female 0       
* `education` - Categorized as tertiles within each study, Centered as middle tertile (-1, 0, 1)  

The DTO has been queried to select relevant variables. The following view gives data for a two individuals:
```{r intro-1, echo=F, results='show', message=FALSE}
```

For the purposes of the current demonstration we fill focus only on the variables that go into computation of the multistate outcome:
```{r intro-2, echo=F, results='show', message=FALSE}
```

## Encode multistate
Now we will demonstrate the logic of encoding
```{r add-logical-variables, echo=T, results='show', message=FALSE, warning = FALSE}
```

### Define function
```{r define-encoding-function, echo=T, results='show', message=FALSE}
```

### Encode outcome
```{r encode-multistate-outcome, echo=TRUE, message=TRUE, warning=TRUE, results='show'}
```

### Inspect created
```{r examine-created-data, echo=T, results='show', message=FALSE}
```

# Recapitulation

```{r save-to-disk, echo=TRUE, results='show', message=FALSE}
```


```{r object-verification, echo=TRUE, results='show', message=FALSE}
```


```{rinspect-created-multistates, echo=TRUE, results='show', message=FALSE}
```


