---
title: "MAP: initial variable review"
output:
  html_document:
    css: ~/GitHub/ialsa-2016-amsterdam/libs/css/sidebar.css
    keep_md: yes
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  warning = FALSE, 
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "960px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 100
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/review-variables/map/review-variables-map.R") 
```



<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```


<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

# (I) Exposition

> This report is a record of interaction with a data transfer object (dto) produced by `./manipulation/map/0-ellis-island-map.R`. 

The next section recaps this script, exposes the architecture of the DTO, and demonstrates the language of interacting with it.   

## (I.A) Ellis Island

> All data land on Ellis Island.

The script `0-ellis-island.R` is the first script in the analytic workflow. It accomplished the following: 

- (1) Reads in raw data file
- (2) Extract, combines, and exports metadata (specifically, variable names and labels, if provided) into `./data/shared/meta/map/names-labels-live.csv`, which is updated every time Ellis Island script is executed.   
- (3) Augments raw metadata with instructions for renaming and classifying variables. The instructions are provided as manually entered values in `./data/shared/meta/map/meta-data-map.csv`. They are used by automatic scripts in later manipulation and analysis.  
- (4) Combines unit and meta data into a single DTO to serve as a starting point to all subsequent analyses.   


<!-- Load the datasets.   -->
```{r load-data, echo=T, results='show', message=FALSE}
```

### Meta
```{r meta-table, echo=TRUE, results='show', message=FALSE}
```


<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```



<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```

<!-- Basic graph view.   -->
```{r basic-graph, echo=TRUE, results='show', message=FALSE}
```

# (II) Development

Details  were requested about the following items (including the availability of treatment for each) :

1. N at each wave
2. Cognitive capability measures
3. Dementia diagnosis
4. Education
5. Social class
6. Physique
7. Smoking  habits
8. Alcohol consumption
9. Social engagement
10. Physical activitiy
11. APOE status
12. Physical capability measures 
13. Cardiovascular disease
14. Hypertension
15. Stroke
16. Diabetes

### General comments

for **all variables** conditions, declare whether they are   
- self reported or diagnosed   
- time variant or invariant (study entry only)   
- treatment or management of the conditions is available  
- provide levels and labels for items with categorical responses   
- specific description of measurement encoding   

## (1) N at each wave

The following pattern of attrition has been observed in the data
```{r B-1-N-at-each-wave, echo=TRUE}
```


## (2) Cognitive capability measures
The following measures of cognitive capability are available in the present instance of MAP data:

```{r B-2-cognitive-1, echo=TRUE}
```

\n\n

Keep for modelling only composite score of cognitive  domains

```{r B-2-cognitive-2, echo=TRUE}
```


```{r B-2-cognitive-3, echo=TRUE, eval=F}
```

In displays below, each cognitive measure is graphed across age (right) and time (left), examining observed trajectories (top row, black lines),  and their linear approximations (bottom row, red lines) with  loess curves (thik blue with ribbon). 
<!-- Individual graphs could be produced with the following script -->
```{r B-2-cognitive-4, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```


### Global
Global cognitive score
```{r B-2-cognitive-5-cogn_global, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```

### Semantic
 Calculated domain score - semantic memory
```{r B-2-cognitive-5-cogn_se, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```


### Episodic 
 Calculated domain score - episodic memory
```{r B-2-cognitive-5-cogn_ep, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```

### Working 
 Calculated domain score - working memory
```{r B-2-cognitive-5-cogn_wo, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```


### Perceptual 
Calculated domain score - perceptual orientation
```{r B-2-cognitive-5-cogn_po, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```

### Speed
 Calculated domain score - perceptual speed
```{r B-2-cognitive-5-cogn_ps, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```

### MMSE 
Mini mental state exam 
```{r B-2-cognitive-5-mmse, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```


## (3) Dementia
 Dementia diagnosis
```{r B-3-dementia-diagnosis, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```


## (4) Education

```{r B-4-education, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```

## (5) Social class
No indicator of social class if found in our version of MAP data

## (6) BMI

```{r B-6-bmi, echo=FALSE, warning=FALSE, message=FALSE, dpi=300}
```
