---
title: 'Estimation: model B'
output:
  html_document:
    css: ~/GitHub/ialsa-2016-amsterdam/libs/css/sidebar.css
    highlight: tango
    keep_md: yes
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "600px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 100
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./manipulation/map/2-estimate-models.R") 
```
This report describes the estimation of **Model B **, specified by the following input:
```{r specify-model, echo=T, results='show', message=FALSE}
```

# I. Exposition

## Environment 
<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=T, message=FALSE}
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=T, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=F, results='show', message=FALSE}
```

## Data 

<!-- Load the datasets.   -->
```{r load-data, echo=T, results='show', message=FALSE}
```

### Encoding
```{r inspect-created-multistates, echo=echoChunks, results='show', message=FALSE}
```

### Cleaning cases
```{r remove-invalid-cases, echo=T, results='show', message=FALSE}
```
### Income
```{r split-income-1, echo=T, results='show', message=FALSE}
```

```{r split-income-2, echo=echoChunks, results='hide', message=FALSE}
```

### Education
```{r split-education-1, echo=T, results='show', message=FALSE}
```

```{r split-education-2, echo=echoChunks, results='hide', message=FALSE}
```

```{r keep-only-legal-states, echo=echoChunks, results='hide', message=FALSE}
```

### Centering
```{r centering-decisions, echo=T, results='show', message=FALSE}
```

### Clean data
```{r prepare-for-estimation, echo=T, results='show', message=FALSE}
```

### Age diagnostic
```{r describe-age-composition, echo=echoChunks, results='show', message=FALSE, eval=T, out.width="900px", out.height="300px"}
```
### Before estimation
```{r inspect-before-estimation, echo=F, results='show', message=FALSE}
```

# II. `msm` estimation

## Functions

The reports used a number of custom function to control the flow of estimation and manipulation

### Fitting 

```{r define-estimation-function, echo=T, results='show', message=FALSE}
```

### Support 

```{r define-support-functions, echo=T, results='show', message=FALSE}
```

## Specifications

### Model 
```{r specify-model, echo=T, results='show', message=FALSE}
```

### Options
```{r specify-msm-options, echo=T, results='show', message=FALSE}
```

## `msm` call
```{r estimate-msm-models, echo=T, results='show', message=FALSE}
```

# III. `ELECT` simulation

## Functions
```{r define-le-functions, echo=T, results='show', message=FALSE}
```

## Options
```{r specify-elect-options, echo=T, results='show', message=FALSE}
```

## `ELECT` calls
### Version 1
```{r compute-life-expectancies-version-1, echo=T, results='show', message=FALSE}
```
### Version 2
```{r compute-life-expectancies-version-2, echo=T, results='show', message=FALSE}
```


# IV. Recapitulation

The estimation routines described above resulted in a series of objects storing information about fitted models
```{r recap-1, echo=T, results='show', message=FALSE}
```

Two version of model B either use a single variable for `education` with values `-1`, `0` and `-1` (`mB_v1`) or two dummy variables `edu_low_med` and `edu_low_high` (`mB_v2`), the definition of which is demonstrated in the exposition. 

The `ELECT` runs simulation for all possible levels in respective `ds_levels` across `min_age` and `max_age` conditions, which are recorded in the suffixes that follow the model code name. To illustrate,
the object `mB_v1_60_110.rds` contains the result of `ELECT` calls for conditional age of `60` with assumed maximum age of `110`.

The structure and interrogation of the objects is demonstrated below
```{r recap-2, echo=T, results='show', message=FALSE}
```


# Session Info
```{r}
sessionInfo()

```


